\bf Summary

### 2025-02-11 paper/paper.qmd
fix affiliations for pdf to render them properly

---
title: "`traveltime`: an R package to calculate walking and motorised travel time from user-specified locations"
format:
  plos-pdf:
    keep-tex: true   
tags: 
  - R
  - geographic information systems
  - spatial analysis
authors:
  - name: Gerard E. Ryan
    orcid: 0000-0003-0183-7630
    corresponding: true
    affiliation: 1, 2
  - name: Nicholas Tierney
    orcid: 0000-0003-1460-8722
    affiliation: 1, 3
  - name: Nick Golding
    orcid: 0000-0001-8916-5570
    affiliation: 1, 4
  - name: Daniel J. Weiss
    orcid: 0000-0002-6175-5648
    affiliation: 1, 3
affiliations:
 - name: The Kids Research Institute Australia, Nedlands 6009 WA, Australia
   index: 1
 - name: Melbourne School of Population and Global Health, University of Melbourne, 3010, VIC, Australia
   index: 2
 - name: Curtin University, Bentley, WA, Australia
   index: 3
 - name: University of Western Australia, WA, Australia
   index: 4
date: In prep 2025
bibliography: paper.bib
---

>>>>

---
title: "`traveltime`: an R package to calculate walking and motorised travel time from user-specified locations"
format:
  plos-pdf:
    keep-tex: true   
tags: 
  - R
  - geographic information systems
  - spatial analysis
authors:
  - name: Gerard E. Ryan
    orcid: 0000-0003-0183-7630
    corresponding: true
    affiliations:
      - The Kids Research Institute Australia, Nedlands 6009 WA, Australia
      - Melbourne School of Population and Global Health, University of Melbourne, 3010, VIC, Australia
  - name: Nicholas Tierney
    orcid: 0000-0003-1460-8722
    affiliations:
      - The Kids Research Institute Australia, Nedlands 6009 WA, Australia
      - Curtin University, Bentley, WA, Australia
  - name: Nick Golding
    orcid: 0000-0001-8916-5570
    affiliations:
      - University of Western Australia, WA, Australia
      - The Kids Research Institute Australia, Nedlands 6009 WA, Australia
  - name: Daniel J. Weiss
    orcid: 0000-0002-6175-5648
    affiliations:
      - The Kids Research Institute Australia, Nedlands 6009 WA, Australia
      - Curtin University, Bentley, WA, Australia
date: In prep 2025
bibliography: paper.bib
---

### 2025-02-11 paper/paper.tex
fix affiliations for pdf to render them properly

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{\texttt{traveltime}: an R package to calculate walking
and motorised travel time from user-specified
locations} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
\\
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
Gerard E. Ryan\textsuperscript{1*}, Nicholas
Tierney\textsuperscript{2}, Nick Golding\textsuperscript{3}, Daniel J.
Weiss\textsuperscript{2}
\\
\bigskip
\textbf{1} 1, 2, \\ \textbf{2} 1, 3, \\ \textbf{3} 1,
4, \\ \textbf{4} The Kids Research Institute Australia, Nedlands 6009
WA, Australia, \\ \textbf{5} Melbourne School of Population and Global
Health, University of Melbourne, 3010, VIC,
Australia, \\ \textbf{6} Curtin University, Bentley, WA,
Australia, \\ \textbf{7} University of Western Australia, WA,
Australia, 
\bigskip

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{\texttt{traveltime}: an R package to calculate walking
and motorised travel time from user-specified
locations} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
\\
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
Gerard E. Ryan\textsuperscript{1,2*}, Nicholas
Tierney\textsuperscript{1,3}, Nick Golding\textsuperscript{4,1}, Daniel
J. Weiss\textsuperscript{1,3}
\\
\bigskip
\textbf{1} The Kids Research Institute Australia, Nedlands 6009 WA,
Australia, \\ \textbf{2} Melbourne School of Population and Global
Health, University of Melbourne, 3010, VIC,
Australia, \\ \textbf{3} Curtin University, Bentley, WA,
Australia, \\ \textbf{4} University of Western Australia, WA,
Australia, 
\bigskip
